Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-18 chapters/discussion/discussion.tex
minor change

In \chapref{whenwhere}, we constructed the constraint function for 
the image capture time and the camera location. In order to achieve
this goal, we trained a CNN on a large dataset that consists of
millions webcam frames and smart phone photos. The network takes image
as input and output the discrete probability over location and time.
In this work, we took the advantage that geo-tagged and
temporal-tagged images are common nowadays to build the training set.
We demonstrate that geo-calibrating the camera helps learn image
representations useful for image understanding.

>>>>

In \chapref{whenwhere}, we developed the constraint function for 
the image capture time and the camera location. 
We trained a CNN on a large dataset to learn to predict the discrete
probabilities over location and time given the input image.
Unlike full supervision methods which require tedious work for manual
annotations, our training dataset consists of millions webcam
frames and smart phone photos with free time/location tags.
In the experiments, we demonstrated that geo-calibrating the camera
also helps learn useful image representations for image understanding.
